---
title: "R Notebook"
output: html_notebook
---

# Equations

1      t01      Cw1
1      t01      (1-Cw1)*Aw1
1      t02      (1-Cw1)*(1-Aw1)
2      t03      Cb1
2      t04      (1-Cb1)*Ab1
2      t03      (1-Cb1)*(1-Ab1)
3      t05      Cp1
3      t05      (1-Cp1)*Aw1
3      t06      (1-Cp1)*(1-Aw1)
4      t07      Cu1
4      t08      (1-Cu1)*Ab1
4      t07      (1-Cu1)*(1-Ab1)
5      t09      Cw1
5      t10     (1-Cw1)*Aw1
5      t09      (1-Cw1)*(1-Aw1)
6      t11     Cb1
6      t11     (1-Cb1)*Ab1
6      t12     (1-Cb1)*(1-Ab1)
7      t13     Cp1
7      t13     (1-Cp1)*Ab1
7      t14     (1-Cp1)*(1-Ab1)
8      t15     Cu1
8      t16     (1-Cu1)*Aw1
8      t15     (1-Cu1)*(1-Aw1)

# White-Compatible: White stimuli

t01: correct responses to White stimuli when White/good share a response key 
t02: incorrect responses to White stimuli when White/good share a response key

1      t01      Cw1
1      t01      (1-Cw1)*Aw1
1      t02      (1-Cw1)*(1-Aw1)

```{r}
t01 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 Cw1 + (1-Cw1)*Aw1
}
t02 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 (1-Cw1)*(1-Aw1)
}
```

# Black-Compatible: Black stimuli

t03: correct responses to Black stimuli when Black/bad share a response key 
t04: incorrect responses to Black stimuli when Black/bad share a response key 

2      t03      Cb1
2      t04      (1-Cb1)*Ab1
2      t03      (1-Cb1)*(1-Ab1)

```{r}
t03 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 Cb1 + (1-Cb1)*(1-Ab1)
}
t04 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 (1-Cb1)*Ab1
}
```

# White-Compatible: Good stimuli

t05: correct responses to good stimuli when White/good share a response key 
t06: incorrect responses to good stimuli when White/good share a response key

3      t05      Cp1
3      t05      (1-Cp1)*Aw1
3      t06      (1-Cp1)*(1-Aw1)

```{r}
t05 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 Cp1 + (1-Cp1)*Aw1
}
t06 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
  (1-Cp1)*(1-Aw1)
}
```

# Black-Compatible: Bad stimuli

t07: correct responses to bad stimuli when Black/bad share a response key 
t08: incorrect responses to bad stimuli when Black/bad share a response key 

4      t07      Cu1
4      t08      (1-Cu1)*Ab1
4      t07      (1-Cu1)*(1-Ab1)

```{r}
t07 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 Cu1 + (1-Cu1)*(1-Ab1)
}
t08 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 (1-Cu1)*Ab1
}
```

# White-Incompatible: White stimuli

t09: correct responses to White stimuli when White/bad share a response key 
t10: incorrect responses to White stimuli when White/bad share a response key

5      t09      Cw1
5      t10     (1-Cw1)*Aw1
5      t09      (1-Cw1)*(1-Aw1)

```{r}
t09 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 Cw1 + (1-Cw1)*(1-Aw1)
}
t10 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 (1-Cw1)*Aw1
}
```

# Black-Incompatible: Black stimuli

t11: correct responses to Black stimuli when Black/good share a response key 
t12: incorrect responses to Black stimuli when Black/good share a response key

6      t11     Cb1
6      t11     (1-Cb1)*Ab1
6      t12     (1-Cb1)*(1-Ab1)

```{r}
t11 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 Cb1 + (1-Cb1)*Ab1
}
t12 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 (1-Cb1)*(1-Ab1)
}
```

# White-Incompatible: Good stimuli

t13: correct responses to good stimuli when White/bad share a response key 
t14: incorrect responses to good stimuli when White/bad share a response key

7      t13     Cp1
7      t13     (1-Cp1)*Ab1
7      t14     (1-Cp1)*(1-Ab1)

```{r}
t13 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 Cp1 + (1-Cp1)*Ab1
}
t14 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
  (1-Cp1)*(1-Ab1)
}
```


# Black-incompatible: Bad stimuli

t15: correct responses to bad stimuli when Black/good share a response key 
t16: incorrect responses to bad stimuli when Black/good share a response key

8      t15     Cu1
8      t16     (1-Cu1)*Aw1
8      t15     (1-Cu1)*(1-Aw1)

```{r}
t15 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 Cu1 + (1-Cu1)*(1-Aw1)
}
t16 <- function(Aw1, Ab1, Cw1, Cb1, Cp1, Cu1){
 (1-Cu1)*Aw1
}
```

# Preparation

```{r}

```


# Calanchini Data Generation

```{r}
path <- "/Volumes/"
setwd(paste0(path,"Research Project/IAT_Retest/Estimates/"))
Cal.Time1<-read.csv("UCR/IndividualParametersPDUCR1.csv", header = T)
Cal.Time2<-read.csv("UCR/IndividualParametersPDUCR2.csv", header = T)
PI.Time1 <- read.csv("PI/IndividualParametersProjectImplicitPD1.csv",header=T)
PI.Time2 <- read.csv("PI/IndividualParametersProjectImplicitPD2.csv",header=T)
Gaw.Time1 <- read.csv("Gawronski/IndividualParametersPDGawronski1.csv",header=T)
Gaw.Time2 <- read.csv("Gawronski/IndividualParametersPDGawronski2.csv",header=T)
For.Time1<-read.csv("Forscher/IndividualParametersForscherPD1.csv", header = T)
For.Time2<-read.csv("Forscher/IndividualParametersForscherPD2.csv", header = T)
Lai1.Time1<-read.csv("Lai1/IndividualParametersLaiStudy1PD1.csv", header = T)
Lai1.Time2<-read.csv("Lai1/IndividualParametersLaiStudy1PD2.csv", header = T)
Lai2.Time1<-read.csv("Lai2/IndividualParametersLaiStudy2PD1.csv", header = T)
Lai2.Time2<-read.csv("Lai2/IndividualParametersLaiStudy2PD2.csv", header = T)

Time1<-grep("Time1",names(.GlobalEnv),value=TRUE)
Time1_list<-do.call("list",mget(Time1))
Time2<-grep("Time2",names(.GlobalEnv),value=TRUE)
Time2_list<-do.call("list",mget(Time2))

paramList <- list(Time1_list, Time2_list)
```

```{r}
set.seed(123)
PDDataGen <- function(df){
Theta1 <- tibble(t01 = t01(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1),
                t02 = t02(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1)
                )
Theta2 <- tibble(t03 = t03(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1),
                t04 = t04(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1)
                )
Theta3 <- tibble(t05 = t05(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1),
                t06 = t06(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1)
                )
Theta4 <- tibble(t07 = t07(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1),
                t08 = t08(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1)
                )
Theta5 <- tibble(t09 = t09(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1),
                t10 = t10(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1)
                )
Theta6 <- tibble(t11 = t11(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1),
                t12 = t12(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1)
                )
Theta7 <- tibble(t13 = t13(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1),
                t14 = t14(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1)
                )
Theta8 <- tibble(t15 = t15(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1),
                t16 = t16(df$Aw1, df$Ab1, df$Cw1, df$Cb1, df$Cp1, df$Cu1)
                )

output <- cbind( t(apply(Theta1, 1, function(x) rmultinom(1,15,x) )),
       t(apply(Theta2, 1, function(x) rmultinom(1,15,x) )),
       t(apply(Theta3, 1, function(x) rmultinom(1,15,x) )),
       t(apply(Theta4, 1, function(x) rmultinom(1,15,x) )),
       t(apply(Theta5, 1, function(x) rmultinom(1,15,x) )),
       t(apply(Theta6, 1, function(x) rmultinom(1,15,x) )),
       t(apply(Theta7, 1, function(x) rmultinom(1,15,x) )),
       t(apply(Theta8, 1, function(x) rmultinom(1,15,x) ))
)

colnames(output) <- c("t01","t02","t03","t04","t05","t06","t07","t08","t09","t10","t11","t12","t13","t14","t15","t16")

return(output)

}

```


```{r}
setwd(paste0(path,"Research Project/IAT_Retest/Recovery/PD_Simulated_Data/"))

for(t in 1:2){
  timeList <- paramList[[t]]
  for(d in 1:length(timeList)){
    df <- timeList[[d]]
    curName <- names(timeList)[d]
    PDdf <- PDDataGen(df)
    write.csv(PDdf, paste0("./",curName,".PDSim.csv"))
  }
}
```

```{r}

```




