---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

# Equations

1      t01      ACwg1
1      t01      (1-ACwg1)*D1
1      t01      (1-ACwg1)*(1-D1)*G1
1      t02      (1-ACwg1)*(1-D1)*(1-G1)
2      t03      ACbb1
2      t03      (1-ACbb1)*D1
2      t04      (1-ACbb1)*(1-D1)*G1
2      t03     (1-ACbb1)*(1-D1)*(1-G1)
3      t05      ACwg1
3      t05      (1-ACwg1)*D1
3      t05      (1-ACwg1)*(1-D1)*G1
3      t06      (1-ACwg1)*(1-D1)*(1-G1)
4      t07      ACbb1
4      t07      (1-ACbb1)*D1
4      t08      (1-ACbb1)*(1-D1)*G1
4      t07      (1-ACbb1)*(1-D1)*(1-G1)
5      t09      ACwg1*D1*OB1
5      t10     ACwg1*D1*(1-OB1)
5      t10     ACwg1*(1-D1)
5      t09      (1-ACwg1)*D1
5      t10     (1-ACwg1)*(1-D1)*G1
5      t09      (1-ACwg1)*(1-D1)*(1-G1)
6      t11     ACbb1*D1*OB1
6      t12     ACbb1*D1*(1-OB1)
6      t12     ACbb1*(1-D1)
6      t11     (1-ACbb1)*D1
6      t11     (1-ACbb1)*(1-D1)*G1
6      t12     (1-ACbb1)*(1-D1)*(1-G1)
7      t14     ACwg1
7      t13     (1-ACwg1)*D1
7      t13     (1-ACwg1)*(1-D1)*G1
7      t14     (1-ACwg1)*(1-D1)*(1-G1)
8      t16     ACbb1
8      t15     (1-ACbb1)*D1
8      t16     (1-ACbb1)*(1-D1)*G1
8      t15     (1-ACbb1)*(1-D1)*(1-G1)

# White-Compatible: White stimuli

t01: correct responses to White stimuli when White/good share a response key 
t02: incorrect responses to White stimuli when White/good share a response key 

1      t01      ACwg1
1      t01      (1-ACwg1)*D1
1      t01      (1-ACwg1)*(1-D1)*G1
1      t02      (1-ACwg1)*(1-D1)*(1-G1)

```{r}
t01 <- function(ACwg, ACbb, D, OB, G){
 ACwg + (1-ACwg)*D + (1 - ACwg)*(1-D)*G
}
t02 <- function(ACwg, ACbb, D, OB, G){
 (1-ACwg)*(1-D)*(1-G)
}
```

# Black-Compatible: Black stimuli

t03: correct responses to Black stimuli when Black/bad share a response key 
t04: incorrect responses to Black stimuli when Black/bad share a response key 

2      t03      ACbb1
2      t03      (1-ACbb1)*D1
2      t04      (1-ACbb1)*(1-D1)*G1
2      t03     (1-ACbb1)*(1-D1)*(1-G1)

```{r}
t03 <- function(ACwg, ACbb, D, OB, G){
 ACbb + (1-ACbb)*D + (1-ACbb)*(1-D)*(1-G)
}
t04 <- function(ACwg, ACbb, D, OB, G){
 (1-ACbb)*(1-D)*G
}
```

# White-Compatible: Good stimuli

t05: correct responses to good stimuli when White/good share a response key 
t06: incorrect responses to good stimuli when White/good share a response key

3      t05      ACwg1
3      t05      (1-ACwg1)*D1
3      t05      (1-ACwg1)*(1-D1)*G1
3      t06      (1-ACwg1)*(1-D1)*(1-G1)

```{r}
t05 <- function(ACwg, ACbb, D, OB, G){
 ACwg + (1-ACwg)*D + (1 - ACwg)*(1-D)*G
}
t06 <- function(ACwg, ACbb, D, OB, G){
 (1-ACwg)*(1-D)*(1-G)
}
```

# Black-Compatible: Bad stimuli

t07: correct responses to bad stimuli when Black/bad share a response key 
t08: incorrect responses to bad stimuli when Black/bad share a response key 

4      t07      ACbb1
4      t07      (1-ACbb1)*D1
4      t08      (1-ACbb1)*(1-D1)*G1
4      t07      (1-ACbb1)*(1-D1)*(1-G1)

```{r}
t07 <- function(ACwg, ACbb, D, OB, G){
 ACbb + (1-ACbb)*D + (1-ACbb)*(1-D)*(1-G)
}
t08 <- function(ACwg, ACbb, D, OB, G){
 (1-ACbb)*(1-D)*G
}
```

# White-Incompatible: White stimuli

t09: correct responses to White stimuli when White/bad share a response key 
t10: incorrect responses to White stimuli when White/bad share a response key

5      t09      ACwg1*D1*OB1
5      t10     ACwg1*D1*(1-OB1)
5      t10     ACwg1*(1-D1)
5      t09      (1-ACwg1)*D1
5      t10     (1-ACwg1)*(1-D1)*G1
5      t09      (1-ACwg1)*(1-D1)*(1-G1)

```{r}
t09 <- function(ACwg, ACbb, D, OB, G){
 ACwg*D*OB + (1-ACwg)*D + (1-ACwg)*(1-D)*(1-G)
}
t10 <- function(ACwg, ACbb, D, OB, G){
 ACwg*D*(1-OB) + ACwg*(1-D) + (1-ACwg)*(1-D)*G
}
```

# Black-Incompatible: Black stimuli

t11: correct responses to Black stimuli when Black/good share a response key 
t12: incorrect responses to Black stimuli when Black/good share a response key

6      t11     ACbb1*D1*OB1
6      t12     ACbb1*D1*(1-OB1)
6      t12     ACbb1*(1-D1)
6      t11     (1-ACbb1)*D1
6      t11     (1-ACbb1)*(1-D1)*G1
6      t12     (1-ACbb1)*(1-D1)*(1-G1)

```{r}
t11 <- function(ACwg, ACbb, D, OB, G){
 ACbb*D*OB + (1-ACbb)*D + (1-ACbb)*(1-D)*G
}
t12 <- function(ACwg, ACbb, D, OB, G){
 ACbb*D*(1-OB) + ACbb*(1-D) + (1-ACbb)*(1-D)*(1-G)
}
```

# White-Incompatible: Good stimuli

t13: correct responses to good stimuli when White/bad share a response key 
t14: incorrect responses to good stimuli when White/bad share a response key

7      t14     ACwg1
7      t13     (1-ACwg1)*D1
7      t13     (1-ACwg1)*(1-D1)*G1
7      t14     (1-ACwg1)*(1-D1)*(1-G1)

```{r}
t13 <- function(ACwg, ACbb, D, OB, G){
 (1-ACwg)*D + (1-ACwg)*(1-D)*G
}
t14 <- function(ACwg, ACbb, D, OB, G){
 ACwg + (1-ACwg)*(1-D)*(1-G)
}
```

# Black-incompatible: Bad stimuli

t15: correct responses to bad stimuli when Black/good share a response key 
t16: incorrect responses to bad stimuli when Black/good share a response key

8      t16     ACbb1
8      t15     (1-ACbb1)*D1
8      t16     (1-ACbb1)*(1-D1)*G1
8      t15     (1-ACbb1)*(1-D1)*(1-G1)

```{r}
t15 <- function(ACwg, ACbb, D, OB, G){
 (1-ACbb)*D + (1-ACbb)*(1-D)*(1-G)
}
t16 <- function(ACwg, ACbb, D, OB, G){
 ACbb + (1-ACbb)*(1-D)*G
}
```

# Preparation

```{r}

```


# Calanchini Data Generation

```{r}
path <- "/Volumes/"
setwd(paste0(path,"Research Project/IAT_Retest/Estimates/"))
Cal.Time1<-read.csv("UCR/IndividualParametersQuadUCR1.csv", header = T)
Cal.Time2<-read.csv("UCR/IndividualParametersQuadUCR2.csv", header = T)
PI.Time1 <- read.csv("PI/IndividualParametersQuadProjectImplicit1.csv",header=T)
PI.Time2 <- read.csv("PI/IndividualParametersQuadProjectImplicit2.csv",header=T)
Gaw.Time1 <- read.csv("Gawronski/IndividualParametersQuadGawronski1.csv",header=T)
Gaw.Time2 <- read.csv("Gawronski/IndividualParametersQuadGawronski2.csv",header=T)
For.Time1<-read.csv("Forscher/IndividualParametersQuadForscher1.csv", header = T)
For.Time2<-read.csv("Forscher/IndividualParametersQuadForscher2.csv", header = T)
Lai1.Time1<-read.csv("Lai1/IndividualParametersLaiStudy1Quad1.csv", header = T)
Lai1.Time2<-read.csv("Lai1/IndividualParametersLaiStudy1Quad2.csv", header = T)
Lai2.Time1<-read.csv("Lai2/IndividualParametersLaiStudy2Quad1.csv", header = T)
Lai2.Time2<-read.csv("Lai2/IndividualParametersLaiStudy2Quad2.csv", header = T)

Time1<-grep("Time1",names(.GlobalEnv),value=TRUE)
Time1_list<-do.call("list",mget(Time1))
Time2<-grep("Time2",names(.GlobalEnv),value=TRUE)
Time2_list<-do.call("list",mget(Time2))

paramList <- list(Time1_list, Time2_list)
```

```{r}
QuadDataGen <- function(df){

Theta1 <- tibble(t01 = t01(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1),
                t02 = t02(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1)
                )
Theta2 <- tibble(t03 = t03(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1),
                t04 = t04(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1)
                )
Theta3 <- tibble(t05 = t05(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1),
                t06 = t06(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1)
                )
Theta4 <- tibble(t07 = t07(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1),
                t08 = t08(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1)
                )
Theta5 <- tibble(t09 = t09(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1),
                t10 = t10(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1)
                )
Theta6 <- tibble(t11 = t11(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1),
                t12 = t12(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1)
                )
Theta7 <- tibble(t13 = t13(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1),
                t14 = t14(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1)
                )
Theta8 <- tibble(t15 = t15(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1),
                t16 = t16(df$ACwg1, df$ACbb1, df$D1, df$OB1, df$G1)
                )

# 1 per participant for 15 choices
N <- 15
output <- cbind( t(apply(Theta1, 1, function(x) rmultinom(1,N,x) )),
       t(apply(Theta2, 1, function(x) rmultinom(1,N,x) )),
       t(apply(Theta3, 1, function(x) rmultinom(1,N,x) )),
       t(apply(Theta4, 1, function(x) rmultinom(1,N,x) )),
       t(apply(Theta5, 1, function(x) rmultinom(1,N,x) )),
       t(apply(Theta6, 1, function(x) rmultinom(1,N,x) )),
       t(apply(Theta7, 1, function(x) rmultinom(1,N,x) )),
       t(apply(Theta8, 1, function(x) rmultinom(1,N,x) ))
)

colnames(output) <- c("t01","t02","t03","t04","t05","t06","t07","t08","t09","t10","t11","t12","t13","t14","t15","t16")

return(output)

}

```


```{r}

set.seed(52)

setwd("/Volumes/GoogleDrive/Shared drives/RSSC Lab/Current Studies/MPT reliability/RepeatedSim/QuadRepeated/")

# number of simulations
iter <- 200

for(t in 1:2){
  timeList <- paramList[[t]]
  for(d in 1:length(timeList)){
    
    for(n in 1:iter){
    df <- timeList[[d]]
    curName <- names(timeList)[d]
    Quaddf <- QuadDataGen(df)
    #dir.create(paste0("./",curName))
    write.csv(Quaddf, paste0("./",curName,"/",curName,".Num",n,".Sim.csv"))
    }
  }
}
```

# Insert Original, True Frequencies

```{r}
# path <- "/Volumes/"
# setwd(paste0(path,"Research Project/IAT_Retest/Estimates/UCR/"))
# Cal.Time1.True<-read.csv("IndividualParametersQuadUCR1.csv", header = T)
# Cal.Time2.True<-read.csv("IndividualParametersQuadUCR2.csv", header = T)
# setwd(paste0(path,"Research Project/IAT_Retest/Estimates/PI/"))
# PI.Time1.True <- read.csv("IndividualParametersQuadProjectImplicit1.csv")
# P1.Time2.True <- read.csv("IndividualParametersQuadProjectImplicit2.csv")
# setwd(paste0(path,"Research Project/IAT_Retest/Estimates/Gawronski/"))
# Gaw.Time1.True <- read.csv("IndividualParametersQuadGawronski1.csv")
# Gaw.Time2.True <- read.csv("IndividualParametersQuadGawronski2.csv")
# setwd(paste0(path,"Research Project/IAT_Retest/Estimates/Forscher/"))
# For.Time1.True<-read.csv("IndividualParametersQuadForscher1.csv", header = T)
# For.Time2.True<-read.csv("IndividualParametersQuadForscher2.csv", header = T)
# setwd(paste0(path,"Research Project/IAT_Retest/Estimates/Lai1/"))
# Lai1.Time1.True<-read.csv("IndividualParametersLaiStudy1Quad1.csv", header = T)
# Lai2.Time2.True<-read.csv("IndividualParametersLaiStudy1Quad2.csv", header = T)
# setwd(paste0(path,"Research Project/IAT_Retest/Estimates/Lai2/"))
# Lai2.Time1.True<-read.csv("IndividualParametersLaiStudy2Quad1.csv", header = T)
# Lai2.Time1.True<-read.csv("IndividualParametersLaiStudy2Quad2.csv", header = T)
```

# Determine How Similar Counts Are With Each Other and With True Counts

```{r}

curDirs <- list.dirs("/Volumes/GoogleDrive/Shared drives/RSSC Lab/Current Studies/MPT reliability/RepeatedSim/QuadRepeated/", recursive = F)

countAssoc <- matrix(ncol=17,nrow=12)

j <- 1
for(i in curDirs){
  setwd(i) # set working directory as current iteration
  curFiles<-list.files(".") # list all files in it
  test<-lapply(curFiles, read.csv) # read in files as list
  curName <- gsub("Num1.Sim.csv","",curFiles[1]) # extract name for files
  countAssoc[j,1] <- curName # assign name to matrix
  for(n in 2:17){
    # bind all simulated DF's nth column, for count data
    curCount <- do.call(cbind, lapply(1:length(curFiles), function(x) cbind(test[[x]][,n]) ) )
    # assign name to the binded counts for the nth column
    assign(paste0(curName,"t",(n-1),"countSims"),curCount)
    # conduct correlations across all columns of counts
    spearCors <- cor(curCount, method="spearman")
    # remove diagonal of 1s which will inflate correlation
    diag(spearCors)=NA
    # assign mean to matrix
    spearMean <- mean(spearCors, na.rm=T)
    countAssoc[j,n] <- spearMean
    

    
    
  }
  j <- j + 1
}

colnames(countAssoc) <- c("Study",paste0("t0",1:9),paste0("t",10:16))
countAssoc <- countAssoc[,c(1,seq(from=2,to=17,by=2))]
countAssoc <- as.data.frame(countAssoc)
countAssoc[,2:ncol(countAssoc)] <- apply(countAssoc[,2:ncol(countAssoc)],2,as.numeric)
write.csv(countAssoc, "~/Documents/GitHub/MPT-Reliability/RepeatedSimulation/output/QuadSpearmanCors.csv",row.names = F)
```






